A free/open-source Kazakh-Tatar machine translation system

### 2013-06-25 paper/paper.tex
new style file and clarification on Tatar verb types

Use of lexc allows for straightforward definition of different word classes and subclasses.  For example, Tatar (but not Kazakh) has two classes of verbs: one which takes a harmonised high vowel in the infinitive (the default), and one which take a harmonised low vowel in the infinitive.  This was implemented in lexc with two similar continuation lexica for verbs: one pointing at a lexicon with an A-initial infinitive ending, and another pointing at a lexicon with an I-initial infinitive ending.

>>>>

Use of lexc allows for straightforward definition of different word classes and subclasses.  For example, Tatar (but not Kazakh) has two classes of verbs: one which takes a harmonised high vowel in the infinitive (the default), and one which takes a harmonised low vowel in the infinitive.  Class membership cannot be predicted based on any phonological criteria and is simply a lexical property of any given verb.  This was implemented in lexc with two similar sets of continuation lexica for verbs: one pointing at a lexicon with an A-initial infinitive ending, and another pointing at a lexicon with an I-initial infinitive ending.  These two sets of continuation lexica are otherwise the same.
